---
title: "Snake River School District: Standardized Test Scores"
output:
  html_document:  
    keep_md: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, include= FALSE}
library(tidyverse)

#3rd Grade
ThirdGrade <- read_csv("Data/CleanThird.csv")

#4th Grade

FourthGrade <- read_csv("Data/CleanFourth.csv")

#5th Grade

FifthGrade <- read_csv("Data/CleanFifth.csv")

#6th Grade

SixthGrade <- read_csv("Data/CleanSixth.csv")

#7th Grade

SeventhGrade <- read_csv("Data/CleanSeventh.csv")

#8th Grade

EighthGrade <- read_csv("Data/CleanEighth.csv")


#10th Grade

TenthGrade <- read_csv("Data/CleanTenth.csv")

```


```{r}
#3rd grade

Prof3Min <- c(2001,2367,2432,2490)

Prof3Max <- c(2366,2431,2489,2811)

#4th grade

Prof4Min <- c(2032,2416,2473, 2533)

Prof4Max <- c(2415,2472,2532,2867)

#5th grade

Prof5Min <- c(2056,2442,2502,2582)

Prof5Max <- c(2441,2501,2581,2916)

#6th grade

Prof6Min <- c(2079, 2257,2531,2618)

Prof6Max <- c(2456,2530,2617,2937)

#7th grade

Prof7Min <- c(2082,2479,2552,2649)

Prof7Max <- c(2478,2552,2648,2964)

#8th grade
Prof8Min <- c(2097,2487,2567,2668)

Prof8Max <- c(2486,2566,2667,2989)

#10th grade

Prof10Min <- c(2102,2491,2577,2677)

Prof10Max <- c(2490,2576,2676,3032)

# Colors
COLORS <- c("#CB0000","#FB6542","#AEBD38", "#598234")
```


## Grades {.tabset}

### 3rd Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scores


```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Reading Scores

```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Writing Scores

```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Listening Scores
```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ListeningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Research Inquiry Scores
```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ResearchInquiryClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Mathematics Scores
```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Concepts And Procedures Scores
```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ConceptsAndProceduresClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Problem Solving And Modeling Data Analysis Scores
```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ProblemSolvingAndModelingDataAnalysisClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Communicating Reasoning Scores

```{r, warning= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = CommunicatingReasoningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof3Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


### 4th Grade {.tabset .tabset-fade .tabset-pills}


#### ELA Literacy Scores


```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Reading Scores

```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Writing Scores

```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Listening Scores
```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ListeningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Research Inquiry Scores
```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ResearchInquiryClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Concepts And Procedures Scores
```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ConceptsAndProceduresClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Problem Solving And Modeling Data Analysis Scores
```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ProblemSolvingAndModelingDataAnalysisClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Communicating Reasoning Scores

```{r, warning= FALSE}
FourthGrade %>%  
  ggplot(aes(y = CommunicatingReasoningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof4Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

### 5th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scores


```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Reading Scores

```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Writing Scores

```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Listening Scores
```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ListeningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Research Inquiry Scores
```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ResearchInquiryClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Concepts And Procedures Scores
```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ConceptsAndProceduresClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Problem Solving And Modeling Data Analysis Scores
```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ProblemSolvingAndModelingDataAnalysisClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Communicating Reasoning Scores

```{r, warning= FALSE}
FifthGrade %>%  
  ggplot(aes(y = CommunicatingReasoningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


### 6th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scores


```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof6Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Reading Scores

```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Writing Scores

```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof6Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Listening Scores
```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ListeningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof6Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Research Inquiry Scores
```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ResearchInquiryClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof6Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Concepts And Procedures Scores
```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ConceptsAndProceduresClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof6Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Problem Solving And Modeling Data Analysis Scores
```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ProblemSolvingAndModelingDataAnalysisClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof6Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Communicating Reasoning Scores

```{r, warning= FALSE}
SixthGrade %>%  
  ggplot(aes(y = CommunicatingReasoningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof6Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

### 7th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scores

```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof7Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Reading Scores

```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Writing Scores

```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof7Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Listening Scores
```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ListeningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof7Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Research Inquiry Scores
```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ResearchInquiryClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof7Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Concepts And Procedures Scores
```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ConceptsAndProceduresClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof7Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Problem Solving And Modeling Data Analysis Scores
```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ProblemSolvingAndModelingDataAnalysisClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof7Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Communicating Reasoning Scores

```{r, warning= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = CommunicatingReasoningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof7Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


### 8th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scores

```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof8Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Reading Scores

```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Writing Scores

```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof8Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Listening Scores
```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ListeningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof8Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Research Inquiry Scores
```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ResearchInquiryClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof8Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Concepts And Procedures Scores
```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ConceptsAndProceduresClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof8Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Problem Solving And Modeling Data Analysis Scores
```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ProblemSolvingAndModelingDataAnalysisClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof8Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Communicating Reasoning Scores

```{r, warning= FALSE}
EighthGrade %>%  
  ggplot(aes(y = CommunicatingReasoningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof8Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


### 10th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scores

```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof10Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Reading Scores

```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof5Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```


#### Writing Scores

```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof10Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Listening Scores
```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ListeningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof10Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Research Inquiry Scores
```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ResearchInquiryClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof10Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Concepts And Procedures Scores
```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ConceptsAndProceduresClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof10Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Problem Solving And Modeling Data Analysis Scores
```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ProblemSolvingAndModelingDataAnalysisClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof10Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```

#### Communicating Reasoning Scores

```{r, warning= FALSE}
TenthGrade %>%  
  ggplot(aes(y = CommunicatingReasoningClaimScaleScore, x = Year))+ 
  geom_jitter()+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  geom_hline(yintercept = Prof10Max, color = COLORS, lty = 2, size = 2)+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Scores")+
  theme_classic()
```



