---
title: "Snake River School District: Standardized Test Scores"
output:
  html_document:  
    keep_md: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
    echo: FALSE
---

```{r, include= FALSE}
library(tidyverse)
library(ggrepel)
library(DT)

#3rd Grade
ThirdGrade <- read_csv("Data/CleanThird.csv")

#4th Grade

FourthGrade <- read_csv("Data/CleanFourth.csv")

#5th Grade

FifthGrade <- read_csv("Data/CleanFifth.csv")

#6th Grade

SixthGrade <- read_csv("Data/CleanSixth.csv")

#7th Grade

SeventhGrade <- read_csv("Data/CleanSeventh.csv")

#8th Grade

EighthGrade <- read_csv("Data/CleanEighth.csv")


#10th Grade

TenthGrade <- read_csv("Data/CleanTenth.csv")

```

On behalf of BYU-Idaho's Data Science Society, we thank you for this opportunity to visualize the trends in the Scale Scores of the Snake River School District. Over the past few months we were able to clean and combine the data for each grade. This made it possible to create [boxplots](https://www.wellbeingatschool.org.nz/information-sheet/understanding-and-interpreting-box-plots) to visualize the change in scores from the 2015/2016 school year to the 2018/2019 school year. Due to discrepancies in the 2014/2015 data, it has been omitted from the analysis.

## Grades {.tabset}

### 3rd Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scale Scores

```{r, warning= FALSE, echo= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of ELA Literacy Scale Scores | Each dot is an individual",
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "ELA Literacy Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
ThirdGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average ELA Literacy Scale Score Over the Years", 
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Average ELA Literacy Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))


```



#### Reading Scale Scores

```{r, warning= FALSE, echo= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Reading Scale Scores | Each dot is an individual",
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Reading Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
ThirdGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Reading Scale Score Over the Years", 
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Average Reading Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```


#### Writing Scale Scores

```{r, warning= FALSE, echo= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Writing Scale Scores | Each dot is an individual",
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Writing Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
ThirdGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Writing Scale Score Over the Years", 
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Average Writing Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Mathematics Scale Scores

```{r, warning= FALSE, echo= FALSE}
ThirdGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Mathematics Scale Scores | Each dot is an individual",
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Mathematics Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
ThirdGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Mathematics Scale Score Over the Years", 
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Average Mathematics Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Comparison

```{r, echo= FALSE}
ThirdGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup() %>% 
  pivot_longer(-Year2, names_to = "Average Scale Scores", values_to = "Average")  %>% 
  ggplot(aes(y = Average, x = Year2, group = `Average Scale Scores`, color = `Average Scale Scores`))+
  geom_point(size = 2)+
  geom_line(size = 1)+
  labs(title = "Average of Scales Scores Over the Years", 
       subtitle = "3rd Grade",
       x = "School Year", 
       y = "Average Scale Scores")+
  scale_color_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))



  
```

```{r, echo= FALSE}
ThirdGrade %>%
  group_by(Year) %>%
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0) 
    )%>%
  ungroup() %>%
    pivot_longer(-Year, names_to = "Label", values_to = "Average") %>%
    ggplot() +
    geom_col(aes(x = Year, y = Average, fill = Label), position = "dodge") +
    coord_cartesian(ylim = c(2300,2500)) +
    theme_bw() +
    scale_fill_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(fill = "Average Scale Scores", 
         x = "School Year", 
         y = "Average Scale Scores", 
         title = "Average of Scale Scores Over the Years",
         subtitle = "3rd Grade") +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))
```




```{r, echo= FALSE}
TableDat<- ThirdGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `Average ELA Scale Score`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Average Reading Scale Score`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Average Writing Scale Score`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Average Math Scale Score`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup()

datatable(TableDat)
```

### 4th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scale Scores

```{r, warning= FALSE, echo= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of ELA Literacy Scale Scores | Each dot is an individual",
       subtitle = "4th Grade",
       x = "School Year", 
       y = "ELA Literacy Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FourthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average ELA Literacy Scale Score Over the Years", 
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Average ELA Literacy Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))


```



#### Reading Scale Scores

```{r, warning= FALSE, echo= FALSE}
FourthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Reading Scale Scores | Each dot is an individual",
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Reading Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FourthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Reading Scale Score Over the Years", 
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Average Reading Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```


#### Writing Scale Scores

```{r, warning= FALSE, echo= FALSE}
FourthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Writing Scale Scores | Each dot is an individual",
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Writing Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FourthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Writing Scale Score Over the Years", 
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Average Writing Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Mathematics Scale Scores

```{r, warning= FALSE, echo= FALSE}
FourthGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Mathematics Scale Scores | Each dot is an individual",
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Mathematics Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FourthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Mathematics Scale Score Over the Years", 
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Average Mathematics Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Comparison

```{r, echo= FALSE}
FourthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup() %>% 
  pivot_longer(-Year2, names_to = "Average Scale Scores", values_to = "Average")  %>% 
  ggplot(aes(y = Average, x = Year2, group = `Average Scale Scores`, color = `Average Scale Scores`))+
  geom_point(size = 2)+
  geom_line(size = 1)+
  labs(title = "Average of Scales Scores Over the Years", 
       subtitle = "4th Grade",
       x = "School Year", 
       y = "Average Scale Scores")+
  scale_color_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))



  
```

```{r, echo= FALSE}
FourthGrade %>%
  group_by(Year) %>%
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0) 
    )%>%
  ungroup() %>%
    pivot_longer(-Year, names_to = "Label", values_to = "Average") %>%
    ggplot() +
    geom_col(aes(x = Year, y = Average, fill = Label), position = "dodge") +
    coord_cartesian(ylim = c(2300,2500)) +
    theme_bw() +
    scale_fill_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(fill = "Average Scale Scores", 
         x = "School Year", 
         y = "Average Scale Scores", 
         title = "Average of Scale Scores Over the Years",
         subtitle = "4th Grade") +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))
```




```{r, echo= FALSE}
TableDat<- FourthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `Average ELA Scale Score`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Average Reading Scale Score`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Average Writing Scale Score`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Average Math Scale Score`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup()

datatable(TableDat)
```

### 5th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scale Scores

```{r, warning= FALSE, echo= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of ELA Literacy Scale Scores | Each dot is an individual",
       subtitle = "5th Grade",
       x = "School Year", 
       y = "ELA Literacy Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FifthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average ELA Literacy Scale Score Over the Years", 
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Average ELA Literacy Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))


```



#### Reading Scale Scores

```{r, warning= FALSE, echo= FALSE}
FifthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Reading Scale Scores | Each dot is an individual",
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Reading Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FifthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Reading Scale Score Over the Years", 
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Average Reading Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```


#### Writing Scale Scores

```{r, warning= FALSE, echo= FALSE}
FifthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Writing Scale Scores | Each dot is an individual",
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Writing Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FifthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Writing Scale Score Over the Years", 
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Average Writing Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Mathematics Scale Scores

```{r, warning= FALSE, echo= FALSE}
FifthGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Mathematics Scale Scores | Each dot is an individual",
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Mathematics Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
FifthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Mathematics Scale Score Over the Years", 
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Average Mathematics Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Comparison

```{r, echo= FALSE}
FifthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup() %>% 
  pivot_longer(-Year2, names_to = "Average Scale Scores", values_to = "Average")  %>% 
  ggplot(aes(y = Average, x = Year2, group = `Average Scale Scores`, color = `Average Scale Scores`))+
  geom_point(size = 2)+
  geom_line(size = 1)+
  labs(title = "Average of Scales Scores Over the Years", 
       subtitle = "5th Grade",
       x = "School Year", 
       y = "Average Scale Scores")+
  scale_color_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))



  
```

```{r, echo= FALSE}
FifthGrade %>%
  group_by(Year) %>%
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0) 
    )%>%
  ungroup() %>%
    pivot_longer(-Year, names_to = "Label", values_to = "Average") %>%
    ggplot() +
    geom_col(aes(x = Year, y = Average, fill = Label), position = "dodge") +
    coord_cartesian(ylim = c(2300,2550)) +
    theme_bw() +
    scale_fill_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(fill = "Average Scale Scores", 
         x = "School Year", 
         y = "Average Scale Scores", 
         title = "Average of Scale Scores Over the Years",
         subtitle = "5th Grade") +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))
```




```{r, echo= FALSE}
TableDat<- FifthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `Average ELA Scale Score`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Average Reading Scale Score`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Average Writing Scale Score`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Average Math Scale Score`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup()

datatable(TableDat)
```

### 6th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scale Scores

```{r, warning= FALSE, echo= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of ELA Literacy Scale Scores | Each dot is an individual",
       subtitle = "6th Grade",
       x = "School Year", 
       y = "ELA Literacy Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SixthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average ELA Literacy Scale Score Over the Years", 
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Average ELA Literacy Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))


```



#### Reading Scale Scores

```{r, warning= FALSE, echo= FALSE}
SixthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Reading Scale Scores | Each dot is an individual",
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Reading Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SixthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Reading Scale Score Over the Years", 
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Average Reading Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```


#### Writing Scale Scores

```{r, warning= FALSE, echo= FALSE}
SixthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Writing Scale Scores | Each dot is an individual",
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Writing Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SixthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Writing Scale Score Over the Years", 
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Average Writing Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Mathematics Scale Scores

```{r, warning= FALSE, echo= FALSE}
SixthGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Mathematics Scale Scores | Each dot is an individual",
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Mathematics Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SixthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Mathematics Scale Score Over the Years", 
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Average Mathematics Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Comparison

```{r, echo= FALSE}
SixthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup() %>% 
  pivot_longer(-Year2, names_to = "Average Scale Scores", values_to = "Average")  %>% 
  ggplot(aes(y = Average, x = Year2, group = `Average Scale Scores`, color = `Average Scale Scores`))+
  geom_point(size = 2)+
  geom_line(size = 1)+
  labs(title = "Average of Scales Scores Over the Years", 
       subtitle = "6th Grade",
       x = "School Year", 
       y = "Average Scale Scores")+
  scale_color_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))



  
```

```{r, echo= FALSE}
SixthGrade %>%
  group_by(Year) %>%
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0) 
    )%>%
  ungroup() %>%
    pivot_longer(-Year, names_to = "Label", values_to = "Average") %>%
    ggplot() +
    geom_col(aes(x = Year, y = Average, fill = Label), position = "dodge") +
    coord_cartesian(ylim = c(2300,2600)) +
    theme_bw() +
    scale_fill_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(fill = "Average Scale Scores", 
         x = "School Year", 
         y = "Average Scale Scores", 
         title = "Average of Scale Scores Over the Years",
         subtitle = "6th Grade") +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))
```




```{r, echo= FALSE}
TableDat<- SixthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `Average ELA Scale Score`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Average Reading Scale Score`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Average Writing Scale Score`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Average Math Scale Score`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup()

datatable(TableDat)
```

### 7th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scale Scores

```{r, warning= FALSE, echo= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of ELA Literacy Scale Scores | Each dot is an individual",
       subtitle = "7th Grade",
       x = "School Year", 
       y = "ELA Literacy Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SeventhGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average ELA Literacy Scale Score Over the Years", 
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Average ELA Literacy Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))


```



#### Reading Scale Scores

```{r, warning= FALSE, echo= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Reading Scale Scores | Each dot is an individual",
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Reading Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SeventhGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Reading Scale Score Over the Years", 
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Average Reading Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```


#### Writing Scale Scores

```{r, warning= FALSE, echo= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Writing Scale Scores | Each dot is an individual",
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Writing Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SeventhGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Writing Scale Score Over the Years", 
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Average Writing Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Mathematics Scale Scores

```{r, warning= FALSE, echo= FALSE}
SeventhGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Mathematics Scale Scores | Each dot is an individual",
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Mathematics Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
SeventhGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Mathematics Scale Score Over the Years", 
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Average Mathematics Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Comparison

```{r, echo= FALSE}
SeventhGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup() %>% 
  pivot_longer(-Year2, names_to = "Average Scale Scores", values_to = "Average")  %>% 
  ggplot(aes(y = Average, x = Year2, group = `Average Scale Scores`, color = `Average Scale Scores`))+
  geom_point(size = 2)+
  geom_line(size = 1)+
  labs(title = "Average of Scales Scores Over the Years", 
       subtitle = "7th Grade",
       x = "School Year", 
       y = "Average Scale Scores")+
  scale_color_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))



  
```

```{r, echo= FALSE}
SeventhGrade %>%
  group_by(Year) %>%
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0) 
    )%>%
  ungroup() %>%
    pivot_longer(-Year, names_to = "Label", values_to = "Average") %>%
    ggplot() +
    geom_col(aes(x = Year, y = Average, fill = Label), position = "dodge") +
    coord_cartesian(ylim = c(2300,2600)) +
    theme_bw() +
    scale_fill_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(fill = "Average Scale Scores", 
         x = "School Year", 
         y = "Average Scale Scores", 
         title = "Average of Scale Scores Over the Years",
         subtitle = "7th Grade") +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))
```




```{r, echo= FALSE}
TableDat<- SeventhGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `Average ELA Scale Score`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Average Reading Scale Score`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Average Writing Scale Score`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Average Math Scale Score`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup()

datatable(TableDat)
```

### 8th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scale Scores

```{r, warning= FALSE, echo= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of ELA Literacy Scale Scores | Each dot is an individual",
       subtitle = "8th Grade",
       x = "School Year", 
       y = "ELA Literacy Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
EighthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average ELA Literacy Scale Score Over the Years", 
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Average ELA Literacy Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))


```



#### Reading Scale Scores

```{r, warning= FALSE, echo= FALSE}
EighthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Reading Scale Scores | Each dot is an individual",
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Reading Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
EighthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Reading Scale Score Over the Years", 
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Average Reading Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```


#### Writing Scale Scores

```{r, warning= FALSE, echo= FALSE}
EighthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Writing Scale Scores | Each dot is an individual",
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Writing Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
EighthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Writing Scale Score Over the Years", 
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Average Writing Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Mathematics Scale Scores

```{r, warning= FALSE, echo= FALSE}
EighthGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Mathematics Scale Scores | Each dot is an individual",
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Mathematics Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
EighthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Mathematics Scale Score Over the Years", 
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Average Mathematics Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Comparison

```{r, echo= FALSE}
EighthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup() %>% 
  pivot_longer(-Year2, names_to = "Average Scale Scores", values_to = "Average")  %>% 
  ggplot(aes(y = Average, x = Year2, group = `Average Scale Scores`, color = `Average Scale Scores`))+
  geom_point(size = 2)+
  geom_line(size = 1)+
  labs(title = "Average of Scales Scores Over the Years", 
       subtitle = "8th Grade",
       x = "School Year", 
       y = "Average Scale Scores")+
  scale_color_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))



  
```

```{r, echo= FALSE}
EighthGrade %>%
  group_by(Year) %>%
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0) 
    )%>%
  ungroup() %>%
    pivot_longer(-Year, names_to = "Label", values_to = "Average") %>%
    ggplot() +
    geom_col(aes(x = Year, y = Average, fill = Label), position = "dodge") +
    coord_cartesian(ylim = c(2300,2600)) +
    theme_bw() +
    scale_fill_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(fill = "Average Scale Scores", 
         x = "School Year", 
         y = "Average Scale Scores", 
         title = "Average of Scale Scores Over the Years",
         subtitle = "8th Grade") +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))
```




```{r, echo= FALSE}
TableDat<- EighthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `Average ELA Scale Score`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Average Reading Scale Score`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Average Writing Scale Score`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Average Math Scale Score`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup()

datatable(TableDat)
```


### 10th Grade {.tabset .tabset-fade .tabset-pills}

#### ELA Literacy Scale Scores

```{r, warning= FALSE, echo= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ElaLiteracyScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of ELA Literacy Scale Scores | Each dot is an individual",
       subtitle = "10th Grade",
       x = "School Year", 
       y = "ELA Literacy Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
TenthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average ELA Literacy Scale Score Over the Years", 
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Average ELA Literacy Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))


```



#### Reading Scale Scores

```{r, warning= FALSE, echo= FALSE}
TenthGrade %>%  
  ggplot(aes(y = ReadingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Reading Scale Scores | Each dot is an individual",
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Reading Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
TenthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Reading Scale Score Over the Years", 
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Average Reading Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```


#### Writing Scale Scores

```{r, warning= FALSE, echo= FALSE}
TenthGrade %>%  
  ggplot(aes(y = WritingClaimScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Writing Scale Scores | Each dot is an individual",
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Writing Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
TenthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Writing Scale Score Over the Years", 
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Average Writing Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Mathematics Scale Scores

```{r, warning= FALSE, echo= FALSE}
TenthGrade %>%  
  ggplot(aes(y = MathematicsScaleScore, x = Year))+ 
  geom_jitter(aes(color = Year), show.legend = FALSE)+
  coord_flip()+
  geom_boxplot(aes(group = Year, alpha = 0.5))+
  guides(alpha = FALSE) +
  labs(title = "Distribution of Mathematics Scale Scores | Each dot is an individual",
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Mathematics Scale Scores")+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))
```


```{r, echo= FALSE}
TenthGrade %>% 
  group_by(Year2) %>% 
  summarise(`AverageScore`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)) %>% 
  ungroup() %>% 
  ggplot(aes(y = `AverageScore`, x = Year2))+
  geom_point()+
  geom_line()+
  labs(title = "Average Mathematics Scale Score Over the Years", 
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Average Mathematics Scale Score")+
  geom_label_repel(aes(label = `AverageScore`, size = 12), show.legend = FALSE)+
  theme_classic() +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13))

```

#### Comparison

```{r, echo= FALSE}
TenthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup() %>% 
  pivot_longer(-Year2, names_to = "Average Scale Scores", values_to = "Average")  %>% 
  ggplot(aes(y = Average, x = Year2, group = `Average Scale Scores`, color = `Average Scale Scores`))+
  geom_point(size = 2)+
  geom_line(size = 1)+
  labs(title = "Average of Scales Scores Over the Years", 
       subtitle = "10th Grade",
       x = "School Year", 
       y = "Average Scale Scores")+
  scale_color_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))



  
```

```{r, echo= FALSE}
TenthGrade %>%
  group_by(Year) %>%
  summarise(
    `ELA Literacy`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Reading`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Writing`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Math`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0) 
    )%>%
  ungroup() %>%
    pivot_longer(-Year, names_to = "Label", values_to = "Average") %>%
    ggplot() +
    geom_col(aes(x = Year, y = Average, fill = Label), position = "dodge") +
    coord_cartesian(ylim = c(2300,2600)) +
    theme_bw() +
    scale_fill_manual(values = c("#375E97","#FB6542", "#FFBB00","#3F681C")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(fill = "Average Scale Scores", 
         x = "School Year", 
         y = "Average Scale Scores", 
         title = "Average of Scale Scores Over the Years",
         subtitle = "10th Grade") +
  theme(axis.title = element_text(size = 13.5),
        axis.text = element_text(size = 12.5),
        plot.title = element_text(hjust = 0.5, size = 14),
        plot.subtitle = element_text(hjust = 0.5, size = 13),
        legend.text = element_text(size = 12.5),
        legend.title = element_text(size = 13.5))
```




```{r, echo= FALSE}
TableDat<- TenthGrade %>% 
  group_by(Year2) %>% 
  summarise(
    `Average ELA Scale Score`= round(mean(ElaLiteracyScaleScore, na.rm = TRUE), 0),
    `Average Reading Scale Score`= round(mean(ReadingClaimScaleScore, na.rm = TRUE), 0),
    `Average Writing Scale Score`= round(mean(WritingClaimScaleScore, na.rm = TRUE), 0),
    `Average Math Scale Score`= round(mean(MathematicsScaleScore, na.rm = TRUE), 0)
    ) %>% 
  ungroup()

datatable(TableDat)
```